On the Bit Complexity of Finding Points in Connected Components of a Smooth Real Hypersurface

### 2020-02-06 main.tex
Update main.tex

  There exists a randomized algorithm that takes $\Gamma, d,$ and $s$
  as input and produces a zero-dimensional parameterization of a set
  that contains at least one point in each connected component of
  $V(f) \cap \R^n$ with probability at least $1/2$. Otherwise the
  algorithm either produces a subset of the points or FAIL. In any
  case, the algorithm uses
  \[
  O^{\sim}(nk(Lb+d^{2n}(s+d)(L+d)))
  \]
  bit operations, with $k \geq -\lg(1-2^{(-1/n)})$. The polynomials in
  the output have degree at most $d^n,$ and height $
  O^{\sim}((s+d)d^n).$
\end{theorem}
The algorithm itself is rather simple. To describe it, we need to
define {\em polar varieties}, which will play a crucial role in this
paper. Let $V=V(f)$, for $f$ as in the theorem. For $i \in
\{1,\hdots,n-1\},$ denote by $\pi_i:\C^n \rightarrow \C^i$ the
projection $(x_1,\hdots,x_n) \mapsto (x_1,\hdots,x_i)$.  The $i$-th
\textit{polar variety} \[W(\pi_i,V) := \{\xb \in V~|~\dim \pi_i(T_\xb
V) < i\}\] is the set of critical points of $\pi_i$ on $V$.  It is
thus defined by the vanishing of \[f,\frac{\pa f}{\pa
  X_{i+1}},\hdots,\frac{\pa f}{\pa X_n}.\]

>>>>

  There exists a randomized algorithm that takes $\Gamma, d,$ and $s$
  as input and produces a zero-dimensional parameterization of a set
  that contains at least one point in each connected component of
  $V(f) \cap \R^n$.

  As part of the randomization, the algorithm chooses a set 
  \[
  S := \{1,2,\hdots,\epsilon^{-2}3n^2(2d)^{2n}\}
  \]
  from which to sample from.

  With probability at least $1-\epsilon$, the output is correct. Otherwise, either a proper subset of the points is produced, or FAIL.  In any case, the algorithm uses
  \[
  O^{\sim}(nk(Lb+d^{2n}(s + \log 1/\epsilon^2+d)(L+d)\log(s + \log 1/\epsilon^2)))
  \]
  bit operations, with $k \geq -\lg(1-(1+\epsilon)^{(-1/n)})$. The polynomials in
  the output have degree at most $d^n,$ and height 
  \[
  O^{\sim}((s+\lg 1/\epsilon^2 + d)d^n)
  =O^{\sim}((s+\lg 1/\epsilon^2)d^{n+1}).
  \]
\end{theorem}

The runtime for cases without a strait-line program in the input are as follows. In these cases a polynomial $f$ of degree $d$ is given in the input, and a strait-line program is built for it by computing all the terms. In this case, $L \geq d^n$ and $b \geq \htt(f) = s,$ so that the number of bit operations becomes
\begin{align*}
      &O^{\sim}(nk(Lb+d^{2n}(s + \log 1/\epsilon^2+d)(L+d)\log(s + \log 1/\epsilon^2)))\\
      &= 
O^{\sim}(nk(d^ns+d^{2n}(s + \log 1/\epsilon^2+d)(d^n+d)\log(s + \log 1/\epsilon^2)))\\
      &= 
O^{\sim}(nk(d^ns+(d^{3n}+d^{2n+1})(s + \log 1/\epsilon^2+d)\log(s + \log 1/\epsilon^2)))\\
     &= 
O^{\sim}(nk(d^{3n}(s + \log 1/\epsilon^2+d)\log(s + \log 1/\epsilon^2)))\\
     &= 
O^{\sim}(nk(d^{3n+1}(s + \log 1/\epsilon^2)\log(s + \log 1/\epsilon^2))),
\end{align*}
and the degree and height of the output does not change.

The algorithm itself is rather simple. To describe it, we need to
define {\em polar varieties}, which will play a crucial role in this
paper. Let $V=V(f)$, for $f$ as in the theorem. For $i \in
\{1,\hdots,n-1\},$ denote by $\pi_i:\C^n \rightarrow \C^i$ the
projection $(x_1,\hdots,x_n) \mapsto (x_1,\hdots,x_i)$.  The $i$-th
\textit{polar variety} \[W(\pi_i,V) := \{\xb \in V~|~\dim \pi_i(T_\xb
V) < i\}\] is the set of critical points of $\pi_i$ on $V$.  It is
thus defined by the vanishing of \[f,\frac{\pa f}{\pa
  X_{i+1}},\hdots,\frac{\pa f}{\pa X_n}.\]
